\problemname{Messy lists}
\noindent
Doris has just started to program and is participating in their first programming competition.
She has encountered a problem that can be solved by sorting some cool integers.
She decides to use the built-in sorting function in the revolutionary new programming language Meowscript.
However, the language isn't finished and its sorting function seems to be a little buggy.

\noindent
Help Doris determine how many elements are in the wrong index in the incorrectly sorted list of integers, compared to the same list if it had been properly sorted in increasing order.

\section*{Input}
\noindent
The first row contains an integer $N$ ($1\leq N \leq 10^6$), the number of elements in the list.
\noindent
The second row contains the $N$ integers $0\leq A_i \leq 10^9$ that make up the incorrectly sorted list.

\section*{Output}
\noindent
Print one integer - the number of elements in the list that are in the wrong position.
\section*{Grading}
\noindent
Your solution will be tested on a number of test-case groups.
\noindent
To receive points for a group, your solution must correctly solve every test-case in the group.

\noindent
\begin{tabular}{| l | l | l |}
\hline
  Group & Point value & Restrictions \\ \hline
  $1$    & $20$       &  $N \leq 2$  \\ \hline 
  $2$    & $20$       &  The built-in sorting function sorts in decreasing order \\ \hline 
  $3$    & $20$       &  $N \leq 1000$ \\ \hline
  $4$    & $40$       &  No further restrictions \\ \hline
\end{tabular}
